\include{preamble}



\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain}

\setcitestyle{square,sort,comma,numbers}
\usepackage{amssymb}% http://ctan.org/pkg/amssymb
\usepackage{pifont}% http://ctan.org/pkg/pifont
\settopmatter{printacmref=false}

\newcommand{\commentty}[1]{{\color{blue} \sf (TY: #1)}}
\newcommand{\commentlh}[1]{{\color{red} \sf (LH: #1)}}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\setcopyright{rightsretained}

\begin{document}


\copyrightyear{2019} 
\acmYear{2019} 
\acmConference[ESEC/FSE '19]{Proceedings of the 27th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{August 26--30, 2019}{Tallinn, Estonia}
\acmBooktitle{Proceedings of the 27th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering (ESEC/FSE '19), August 26--30, 2019, Tallinn, Estonia}\acmDOI{10.1145/3338906.3342497}
\acmISBN{978-1-4503-5572-8/19/08}
	
\title{Analysing Socio-Technical Congruence in\\ the Package Dependency Network of Cargo}

	\author{Mehdi Golzadeh}
	\email{mehdi.golzadeh@umons.ac.be}
	\orcid{0000-0003-1041-439X}
	\affiliation{%
	\institution{Software Engineering Lab, UMONS}
	\city{Mons, Belgium}
	\postcode{7000}
	}
	
	\newcommand*{\Scale}[2][4]{\scalebox{#1}{$#2$}}%
	\newcommand{\Tool}{ComAir\xspace}
	\newcommand{\ComBugs}{30\xspace}
	%\newcommand{\Code}[1]{\lstinline{#1}}
	%\newcommand{\comment}[1]{{}}
	
	
	
	
	
\begin{abstract}
Today's software development heavily relies on open source components distributed through software package managers such as Cargo for the Rust programming language. Such packages form large dependency networks, and are maintained by large communities of contributors. Little is known however, about the interplay between the social and technical activities of these packages and their contributors. My PhD research will consist of temporally analysing such socio-technical congruence on an ecosystem-wide scale, and studying its impact on the health of the ecosystem and its community.
I have started a longitudinal empirical study of Cargo's package dependency network and the social (commenting) and technical (development) activities in Cargo’s package repositories on GitHub. I present some preliminary findings based on over a decade of historical data for nearly 10k Cargo packages and their associated GitHub repositories.
\end{abstract}
	
\maketitle
	
\input{Introduction.tex}
\input{Related.tex}
\input{Methodology.tex}
\input{Findings.tex}
\input{Conclusion.tex}

%\section*{Acknowledgment}
\textbf{Acknowledgement.} This research is supported by the joint FNRS / FWO Excellence of Science project 30446992 SECO-ASSIST.

\newpage
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio.bib}



\end{document}
